---
title: "Dynamic Plots"
author: "Collin Owens"
format: html
editor: visual
---

```{r}
library(lubridate)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(ggthemes)
library(httr)
library(rlist)
library(jsonlite)
library(plotly)
library(dygraphs)
library(xts)
library(htmlwidgets)
library(tidyverse)
```

#Setting Dataset up
```{r}
LAD <- VERB("GET", url = "https://www.lostarkmarket.online/api/export-item-history/North America West/basic-oreha-fusion-material-2,crystallized-destruction-stone-0,crystallized-guardian-stone-0,great-honor-leapstone-2,honor-shard-pouch-l-3,honor-shard-pouch-m-2,honor-shard-pouch-s-1,solar-blessing-2,solar-grace-1,solar-protection-3", encode = "json")

resptxt <- content(LAD, as="text")

Converting <- fromJSON(resptxt)

LostArkData <- Converting%>%bind_rows%>%select(id,timestamp,open,close,high,low)

attach(LostArkData)

#converting nonsensical time into real dates and replacing the old ones with a real date.
Tconvert <- timestamp/1000
Newtime <- as_date(as_datetime(Tconvert))
LostArkData$timestamp <- Newtime

#Removing any price=0 because the minimum price will always be 1
LostArkData$open[LostArkData$open ==0] <- NA
LostArkData$close[LostArkData$close ==0] <- NA
LostArkData$high[LostArkData$high ==0] <- NA
LostArkData$low[LostArkData$low ==0] <- NA
LostArkData <- LostArkData[complete.cases(LostArkData), ]

#checking new length, looks like we have removed 4 observations.
length(LostArkData$id)

#renaming first 2 columns
names(LostArkData)[1] <- "Item"
names(LostArkData)[2] <- "Date"

#renaming observations to in game names.
LostArkData$Item[LostArkData$Item == "basic-oreha-fusion-material-2"] <- "Basic Oreha"
LostArkData$Item[LostArkData$Item == "crystallized-destruction-stone-0"] <- "Destruction Stone"
LostArkData$Item[LostArkData$Item == "crystallized-guardian-stone-0"] <- "Guardian Stone"
LostArkData$Item[LostArkData$Item == "great-honor-leapstone-2"] <- "Great Honor Leapstones"
LostArkData$Item[LostArkData$Item == "honor-shard-pouch-l-3"] <- "Honor Shard L"
LostArkData$Item[LostArkData$Item == "honor-shard-pouch-m-2"] <- "Honor Shard M"
LostArkData$Item[LostArkData$Item == "honor-shard-pouch-s-1"] <- "Honor Shard S"
LostArkData$Item[LostArkData$Item == "solar-blessing-2"] <- "Solar Blessing"
LostArkData$Item[LostArkData$Item == "solar-grace-1"] <- "Solar Grace"
LostArkData$Item[LostArkData$Item == "solar-protection-3"] <- "Solar Protection"
```


#Cleaning and separating
I have to separate each data set into its own thing for the plots to play nice with eachother.
```{r}
LostArkData <- LostArkData[!(LostArkData$open == 65.00 & LostArkData$high == 14899.00),]
LostArkData <- LostArkData[!(LostArkData$open == 13.00 & LostArkData$high == 2500.00),]
LostArkData <- LostArkData[!(LostArkData$open == 187.00 & LostArkData$high == 1823.00),]
LostArkData <- LostArkData[!(LostArkData$open == 1823.00 & LostArkData$high == 1823.00),]

LostArkData <- LostArkData[!(LostArkData$open == 118.00 & LostArkData$low == 11.00),]
LostArkData <- LostArkData[!(LostArkData$close == 116.00 & LostArkData$low == 11.00),]
LostArkData <- LostArkData[!(LostArkData$open == 116.00 & LostArkData$low == 11.00),]
LostArkData <- LostArkData[!(LostArkData$close == 115.00 & LostArkData$low == 11.00),]

#LAGHLD is a data set for Great Honor Leapstones
LAGHLD <- LostArkData %>% filter(LostArkData$Item %in% c("Great Honor Leapstones"))

#LAOrehaD is a data set for Oreha material.
LAOrehaD <- LostArkData %>% filter(LostArkData$Item %in% c("Basic Oreha"))

#LADGD T3 Destruction and T3 Guardians
LADestructionD <- LostArkData %>% filter(LostArkData$Item %in% c("Destruction Stone"))
LAGuardianD <- LostArkData %>% filter(LostArkData$Item %in% c("Guardian Stone"))

#LARateupD is a data set for rate up materials 
LABlessingD <- LostArkData %>% filter(LostArkData$Item %in% c("Solar Blessing"))
LAGraceD <- LostArkData %>% filter(LostArkData$Item %in% c("Solar Grace"))
LAProtectionD <- LostArkData %>% filter(LostArkData$Item %in% c("Solar Protection"))

#LAShardsD is a data set for the shard packs
LALShardD <- LostArkData %>% filter(LostArkData$Item %in% c("Honor Shard L"))
LAMShardD <- LostArkData %>% filter(LostArkData$Item %in% c("Honor Shard M"))
LASShardD <- LostArkData %>% filter(LostArkData$Item %in% c("Honor Shard S"))


#Shaded regions
Shade <- data.frame(start = as.Date(c('2022-04-25','2022-05-06','2022-06-01','2022-07-12','2022-07-29','2022-09-20')), end = as.Date(c('2022-04-28','2022-05-19','2022-06-30','2022-07-19','2022-08-15','2022-09-28')))

Shade1 <- data.frame(start = as.Date(c('2022-07-12','2022-07-29','2022-09-20')), end = as.Date(c('2022-07-19','2022-08-15','2022-09-28')))
```

#New Data transformation
This is done for having specific date data, the old data had about 12+ observations per date but the High, Low, Close data is not displayed as nice if we do not separate the dates out. 
```{r}
#Great honor data
Open <- LAGHLD %>% group_by(Date) %>% slice_head()
Close <- LAGHLD %>% group_by(Date) %>% slice_tail()
Min <- LAGHLD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LAGHLD %>% group_by(Date) %>% arrange(low) %>%slice_tail
id <- 1:length(Close$close)

NGHLD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NGHLD)[1] <- "Item"
names(NGHLD)[2] <- "Date"
names(NGHLD)[3] <- "Open"
names(NGHLD)[4] <- "Close"
names(NGHLD)[5] <- "Min"
names(NGHLD)[6] <- "Max"


#Oreha
Open <- LAOrehaD %>% group_by(Date) %>% slice_head()
Close <- LAOrehaD %>% group_by(Date) %>% slice_tail()
Min <- LAOrehaD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LAOrehaD %>% group_by(Date) %>% arrange(low) %>%slice_tail
id <- 1:length(Close$close)

NOrehaD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NOrehaD)[1] <- "Item"
names(NOrehaD)[2] <- "Date"
names(NOrehaD)[3] <- "Open"
names(NOrehaD)[4] <- "Close"
names(NOrehaD)[5] <- "Min"
names(NOrehaD)[6] <- "Max"

#Destruction
Open <- LADestructionD %>% group_by(Date) %>% slice_head()
Close <- LADestructionD %>% group_by(Date) %>% slice_tail()
Min <- LADestructionD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LADestructionD %>% group_by(Date) %>% arrange(low) %>% slice_tail
id2 <- 1:length(Close$close)

NDestructionD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id2)
names(NDestructionD)[1] <- "Item"
names(NDestructionD)[2] <- "Date"
names(NDestructionD)[3] <- "Open"
names(NDestructionD)[4] <- "Close"
names(NDestructionD)[5] <- "Min"
names(NDestructionD)[6] <- "Max"

#Guardian
Open <- LAGuardianD %>% group_by(Date) %>% slice_head()
Close <- LAGuardianD %>% group_by(Date) %>% slice_tail()
Min <- LAGuardianD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LAGuardianD %>% group_by(Date) %>% arrange(low) %>%slice_tail
id2 <- 1:length(Close$close)

NGuardianD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id2)
names(NGuardianD)[1] <- "Item"
names(NGuardianD)[2] <- "Date"
names(NGuardianD)[3] <- "Open"
names(NGuardianD)[4] <- "Close"
names(NGuardianD)[5] <- "Min"
names(NGuardianD)[6] <- "Max"

#Solar Blessings
Open <- LABlessingD %>% group_by(Date) %>% slice_head()
Close <- LABlessingD %>% group_by(Date) %>% slice_tail()
Min <- LABlessingD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LABlessingD %>% group_by(Date) %>% arrange(low) %>%slice_tail

NBlessingD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NBlessingD)[1] <- "Item"
names(NBlessingD)[2] <- "Date"
names(NBlessingD)[3] <- "Open"
names(NBlessingD)[4] <- "Close"
names(NBlessingD)[5] <- "Min"
names(NBlessingD)[6] <- "Max"

#Solar Grace
Open <- LAGraceD %>% group_by(Date) %>% slice_head()
Close <- LAGraceD %>% group_by(Date) %>% slice_tail()
Min <- LAGraceD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LAGraceD %>% group_by(Date) %>% arrange(low) %>%slice_tail

NGraceD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NGraceD)[1] <- "Item"
names(NGraceD)[2] <- "Date"
names(NGraceD)[3] <- "Open"
names(NGraceD)[4] <- "Close"
names(NGraceD)[5] <- "Min"
names(NGraceD)[6] <- "Max"

#Solar Protection
Open <- LAProtectionD %>% group_by(Date) %>% slice_head()
Close <- LAProtectionD %>% group_by(Date) %>% slice_tail()
Min <- LAProtectionD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LAProtectionD %>% group_by(Date) %>% arrange(low) %>%slice_tail

NProtectionD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NProtectionD)[1] <- "Item"
names(NProtectionD)[2] <- "Date"
names(NProtectionD)[3] <- "Open"
names(NProtectionD)[4] <- "Close"
names(NProtectionD)[5] <- "Min"
names(NProtectionD)[6] <- "Max"

#Large Shards 
Open <- LALShardD %>% group_by(Date) %>% slice_head()
Close <- LALShardD %>% group_by(Date) %>% slice_tail()
Min <- LALShardD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LALShardD %>% group_by(Date) %>% arrange(low) %>%slice_tail

NLShardD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NLShardD)[1] <- "Item"
names(NLShardD)[2] <- "Date"
names(NLShardD)[3] <- "Open"
names(NLShardD)[4] <- "Close"
names(NLShardD)[5] <- "Min"
names(NLShardD)[6] <- "Max"

#Medium Shards 
Open <- LAMShardD %>% group_by(Date) %>% slice_head()
Close <- LAMShardD %>% group_by(Date) %>% slice_tail()
Min <- LAMShardD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LAMShardD %>% group_by(Date) %>% arrange(low) %>%slice_tail

NMShardD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NMShardD)[1] <- "Item"
names(NMShardD)[2] <- "Date"
names(NMShardD)[3] <- "Open"
names(NMShardD)[4] <- "Close"
names(NMShardD)[5] <- "Min"
names(NMShardD)[6] <- "Max"

#Small Shards 
Open <- LASShardD %>% group_by(Date) %>% slice_head()
Close <- LASShardD %>% group_by(Date) %>% slice_tail()
Min <- LASShardD %>% group_by(Date) %>% arrange(high) %>%slice_head
Max <- LASShardD %>% group_by(Date) %>% arrange(low) %>%slice_tail

NSShardD <- data.frame(Open$Item,Open$Date,Open$open,Close$close,Min$low,Max$high,id)
names(NSShardD)[1] <- "Item"
names(NSShardD)[2] <- "Date"
names(NSShardD)[3] <- "Open"
names(NSShardD)[4] <- "Close"
names(NSShardD)[5] <- "Min"
names(NSShardD)[6] <- "Max"

#Giant merge of single day market descriptions
NLAD <- rbind(NGHLD,NOrehaD,NBlessingD,NGraceD,NBlessingD,NProtectionD,NLShardD,NMShardD,NSShardD)
NStonesD <- rbind(NDestructionD,NGuardianD)
```

#Regrouping for use in new GGPlot graphs
These are for if I want to combine the data together for multiple items on a graph like the static graphs
```{r}
#LADGD T3 Destruction, T3 Guardians
NDGD <- NStonesD %>% filter(NStonesD$Item %in% c("Destruction Stone","Guardian Stone"))

#LARateupD is a data set for rate up materials 
NRateupD <- NLAD %>% filter(NLAD$Item %in% c("Solar Blessing","Solar Grace","Solar Protection"))

#LAShardsD is a data set for the shard packs
NShardsD <- NLAD %>% filter(NLAD$Item %in% c("Honor Shard L","Honor Shard M","Honor Shard S"))
```



#First graphs
With separating the data I can now make a candlestick chart of any single item. 
```{r}
GHLCgraph <- NGHLD %>% plot_ly(x = ~Date, type="candlestick",
          open = ~Open, close = ~Close,
          high = ~Max, low = ~Min) 

GHLCgraph
```


#Plotly line graph setup.
```{r}
GHLLine <- plot_ly(NGHLD, x = ~Date, y= ~Close, type = 'scatter', mode = 'lines', name = "Great Honor Leapstone") %>% layout(hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date")))

OrehaLine <- plot_ly(NOrehaD, x = ~Date, y= ~Close, type = 'scatter', mode = 'lines', name = "Basic Oreha Material") %>% layout(hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date")))

StoneLine <- plot_ly() %>% layout(hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date"))) %>%
  add_trace(x = NDestructionD$Date, y = NDestructionD$Close, type = 'scatter', mode = 'line', name = "Destruction", line = list(color = 'red')) %>%
  add_trace(x = NGuardianD$Date, y = NGuardianD$Close, type = 'scatter', mode = 'line', name = "Guardian", line = list(color = 'blue'))

ShardsLine <- plot_ly() %>% layout(hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date"))) %>%
  add_trace(x = NLShardD$Date, y = NLShardD$Close, type = 'scatter', mode = 'line', name = "Large pouch", line = list(color = 'red')) %>%
  add_trace(x = NMShardD$Date, y = NMShardD$Close, type = 'scatter', mode = 'line', name = "Medium pouch", line = list(color = 'blue')) %>%
  add_trace(x = NSShardD$Date, y = NSShardD$Close, type = 'scatter', mode = 'line', name = "Small pouch", line = list(color = 'Green'))

RateupLine <- plot_ly() %>% layout(hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date"))) %>%
  add_trace(x = NProtectionD$Date, y = NProtectionD$Close, type = 'scatter', mode = 'line', name = "Solar Protection", line = list(color = 'red')) %>%
  add_trace(x = NBlessingD$Date, y = NBlessingD$Close, type = 'scatter', mode = 'line', name = "Solar Blessing", line = list(color = 'blue')) %>%
  add_trace(x = NGraceD$Date, y = NGraceD$Close, type = 'scatter', mode = 'line', name = "Solar Grace", line = list(color = 'green')) 

#Super Graph for fun
SuperLine <- plot_ly() %>% layout(hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date"))) %>%
  add_trace(x = NProtectionD$Date, y = NProtectionD$Close, type = 'scatter', mode = 'line', name = "Solar Protection", line = list(color = 'rgb(255, 153, 51)')) %>%
  add_trace(x = NBlessingD$Date, y = NBlessingD$Close, type = 'scatter', mode = 'line', name = "Solar Blessing", line = list(color = 'rgb(0, 204, 204)')) %>%
  add_trace(x = NGraceD$Date, y = NGraceD$Close, type = 'scatter', mode = 'line', name = "Solar Grace", line = list(color = 'rgb(0, 204, 102)')) %>%
  add_trace(x = NLShardD$Date, y = NLShardD$Close, type = 'scatter', mode = 'line', name = "Large pouch", line = list(color = 'rgb(255, 0, 0)')) %>%
  add_trace(x = NMShardD$Date, y = NMShardD$Close, type = 'scatter', mode = 'line', name = "Medium pouch", line = list(color = 'rgb(0, 0, 255)')) %>%
  add_trace(x = NSShardD$Date, y = NSShardD$Close, type = 'scatter', mode = 'line', name = "Small pouch", line = list(color = 'rgb(51, 102, 0)')) %>%
  add_trace(x = NOrehaD$Date, y = NOrehaD$Close, type = 'scatter', mode = 'line', name = "Oreha Material", line = list(color = 'rgb(0, 0, 0)')) %>%
  add_trace(x = NGHLD$Date, y = NGHLD$Close, type = 'scatter', mode = 'line', name = "Great Honor Leapstones", line = list(color = 'rgb(255, 0, 127)'))
```

#Plotly Line Graphs
```{r}
GHLLine

OrehaLine

StoneLine

ShardsLine

RateupLine

#All items but stones included for fun
SuperLine
```
#Buttons for Shading regions
```{r}
Region1 <- list(type = 'rect', xref = 'x', yref = 'y', y0 = 0, y1 = 800, x0=Shade[1,1], x1=Shade[1,2], opacity = .2, fillcolor = "gray")
Region2 <- list(type = 'rect', xref = 'x', yref = 'y', y0 = 0, y1 = 800, x0=Shade[2,1], x1=Shade[2,2], opacity = .2, fillcolor = "gray")
Region3 <- list(type = 'rect', xref = 'x', yref = 'y', y0 = 0, y1 = 800, x0=Shade[3,1], x1=Shade[3,2], opacity = .2, fillcolor = "gray")
Region4 <- list(type = 'rect', xref = 'x', yref = 'y', y0 = 0, y1 = 800, x0=Shade[4,1], x1=Shade[4,2], opacity = .2, fillcolor = "gray")
Region5 <- list(type = 'rect', xref = 'x', yref = 'y', y0 = 0, y1 = 800, x0=Shade[5,1], x1=Shade[5,2], opacity = .2, fillcolor = "gray")
Region6 <- list(type = 'rect', xref = 'x', yref = 'y', y0 = 0, y1 = 800, x0=Shade[6,1], x1=Shade[6,2], opacity = .2, fillcolor = "gray")

updatemenus <- list(
  list(
    active = -1,
    type = 'buttons',
    buttons = list(

      list(
        label = "None",
        method = "relayout",
        args = list(list(shapes = c()))),

      list(
        label = "Hyper Express 1",
        method = "relayout",
        args = list(list(shapes = list(Region1, c(),c(), c(),c(),c())))),
      
      list(
        label = "May Update",
        method = "relayout",
        args = list(list(shapes = list(c(),Region2,c(), c(),c(),c())))),
      
      list(
        label = "June/July Update",
        method = "relayout",
        args = list(list(shapes = list(c(),c(), Region3,c(),c(),c())))),
      
      list(
        label = "Hyper Express 2",
        method = "relayout",
        args = list(list(shapes = list(c(),c(),c(),Region4,c(),c())))),
      
      list(
        label = "August update",
        method = "relayout",
        args = list(list(shapes = list(c(),c(),c(), c(),c(),Region5,c())))),
      
      list(
        label = "Clown update",
        method = "relayout",
        args = list(list(shapes = list(c(),c(),c(), c(),c(),c(),Region6)))),
      
      list(
        label = "All",
        method = "relayout",
        args = list(list(shapes = list(c(),Region1,Region2, Region3,Region4,Region5,Region6))))
      
    )))



GHLLine <- plot_ly(NGHLD, x = ~Date, y= ~Close, type = 'scatter', mode = 'lines', name = "Great Honor Leapstone") %>% layout(updatemenus = updatemenus, hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date")))


GHLLine

```

```{r}
SuperLine <- plot_ly() %>% layout(updatemenus = updatemenus, hovermode = "x", yaxis = list(title = "Price in gold"),xaxis = list(
    rangeselector = list(
      buttons = list(
        list(
          count = 7,
          label = "1 Week",
          step = "day",
          stepmode = "backward"),
        list(
          count = 1,
          label = "1 month",
          step = "month",
          stepmode = "backward"),list(step = "all"))), 
    rangeslider = list(type = "date"))) %>%
  add_trace(x = NProtectionD$Date, y = NProtectionD$Close, type = 'scatter', mode = 'line', name = "Solar Protection", line = list(color = 'rgb(255, 153, 51)')) %>%
  add_trace(x = NBlessingD$Date, y = NBlessingD$Close, type = 'scatter', mode = 'line', name = "Solar Blessing", line = list(color = 'rgb(0, 204, 204)')) %>%
  add_trace(x = NGraceD$Date, y = NGraceD$Close, type = 'scatter', mode = 'line', name = "Solar Grace", line = list(color = 'rgb(0, 204, 102)')) %>%
  add_trace(x = NLShardD$Date, y = NLShardD$Close, type = 'scatter', mode = 'line', name = "Large pouch", line = list(color = 'rgb(255, 0, 0)')) %>%
  add_trace(x = NMShardD$Date, y = NMShardD$Close, type = 'scatter', mode = 'line', name = "Medium pouch", line = list(color = 'rgb(0, 0, 255)')) %>%
  add_trace(x = NSShardD$Date, y = NSShardD$Close, type = 'scatter', mode = 'line', name = "Small pouch", line = list(color = 'rgb(51, 102, 0)')) %>%
  add_trace(x = NOrehaD$Date, y = NOrehaD$Close, type = 'scatter', mode = 'line', name = "Oreha Material", line = list(color = 'rgb(0, 0, 0)')) %>%
  add_trace(x = NGHLD$Date, y = NGHLD$Close, type = 'scatter', mode = 'line', name = "Great Honor Leapstones", line = list(color = 'rgb(255, 0, 127)'))

SuperLine
```

